Twitter Data Analysis

### 2019-05-04 csci260/wordCountingApp/twitter.tex
Finished my section?
> Removed Twitter API portion, as it is unnecessary and the info is included in Methodology
> Finished Methodology section
> Added citations

\section{Methodology}
\tab ***David Write your stuff here***

\section{Twitter API}
\tab ***David Write your stuff here***

@@

\newpage
\begin{thebibliography}{}
	\bibitem{stuff}I don't think we need any references, do we?

>>>>

\section{Methodology}
\tab In order to collect the tweet data for the analysis, this study chose to use the Twitter API [2]. This required a twitter developer account, and security keys to access the API using HTTP requests. A twitter developer was created, and the project was registered under Twitter to get the access keys.
\tab After aquiring the access keys, the project utilized the command line program "Twurl" to send Twitter search requests to the API. Results were returned in a json file format. Unfortunately, because the project didn't aquire the premium form of the Twitter API, each search request was limited to 15 results.
\tab Because of this, the project was instead composed of a hundred seperate search requests, using Wikipedia's list of the most common words in english [3]. Then, a python script was created to parse the json files retrieved, and search the tweets for the profane words. Finally, the collected data was used to create tables and support our conclusion.

@@

\newpage
\begin{thebibliography}{}
	\bibitem{Twitter}
	Twitter. (2019). It's what's happening.
	Retrieved from {https://twitter.com}

	\bibitem{Twitter API Reference}
	Twitter. (2019). Developer Documentation.
	Retrieved from {https://developer.twitter.com/en/docs.html}

	\bibitem{Wikipedia}
	Wikimedia Foundation. (2018, December 12). Most common words in English. 
	Retrieved from {https://en.wikipedia.org/wiki/Most_common_words_in_English}
